Flexibility of interactions depends on habitat suitability

### 2019-09-01 paper/manuscript.Rmd
Specify we're talking about the eltonian niche in first paragraph
Change first paragraph, make it even more broad

From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
On one end of the spectrum, generalist species have traits that allow them to interact with a large number of species.
In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
On the other end of the spectrum, specialist species are thought to have a more deep-rooted co-evolutionary history with their partner species. 
This tighter co-evolution, in turn, can be reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
This niche-based rationale can also operate within a species. 
We can expect that a species can obtain a higher benefit from interactions with species with traits that better match their requirements.

>>>>

Species interactions are known to vary widely across space and time. 
There are multiple examples of species that interact tightly in an ecological community or a particular season but not in another. 
It is crucial to understand why and how this turnover of interactions occur because the network of interactions of an ecological community is known to underpin ecosystem function and stability. 
Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another. 
From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
On one end of the spectrum, generalist species have traits that allow them to interact with a large number of species.
In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
On the other end of the spectrum, specialist species are thought to have a more deep-rooted co-evolutionary history with their partner species. 
This tighter co-evolution, in turn, can be reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
This "Eltionian" niche-based rationale can also operate within a species. 
We can expect that a species can obtain a higher benefit from interactions with species with traits that better match their requirements.
